Challenges to the Two-Infall Scenario by Large Stellar Age Catalogs

### 2025-07-03 src/tex/ms.tex
Updates from Overleaf

>>>>

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{figures/smooth_vs_twoinfall.pdf}
    \caption{Chemical abundance tracks predicted by a two-infall model at $R_{\rm gal}=8\kpc$ (solid curve) versus a model with a smooth SFH at three different radii (dashed curves). The two-infall model adopts the fiducial parameters according to Table \ref{tab:multizone-parameters}, while the smooth SFH adopts the parameters of the ``inside-out'' model of \citet{johnson_stellar_2021}. Both models assume the \yZ{2} yield scale (see Table \ref{tab:yields}). The 2-D histogram shows the number of stars from APOGEE DR17 in each bin of ([Fe/H], [O/Fe]).}
    \label{fig:smooth-vs-twoinfall}
\end{figure}
